Division and Slope Factorization of p-Adic Polynomials

### 2016-06-20 polynomials/slopefact.tex
Updates to paper for submission, staying within 8 pages

\CopyrightYear{2016}
\setcopyright{licensedothergov}
\conferenceinfo{ISSAC'16,}{July 19--22, 2016, Waterloo, ON, Canada} \isbn{978-1-4503-4380-0/16/07}
\acmPrice{\$15.00}
\doi{http://dx.doi.org/10.1145/2930889.2930897}

\permission{Publication rights licensed to ACM. ACM acknowledges that this contribution was authored or co-authored by an employee, contractor or affiliate of a national government. As such, the Government retains a nonexclusive, royalty-free right to publish or reproduce this article, or to allow others to do so, for Government purposes only.}

@@

\numberofauthors{3}
\author{
\alignauthor Xavier Caruso\\
  \affaddr{Universit\'e Rennes 1}\\
  \affaddr{\textsf{xavier.caruso@normalesup.org}}
\alignauthor David Roe \\
  \affaddr{University of Pittsburgh}\\
  \affaddr{\textsf{roed.math@gmail.com}}
\alignauthor Tristan Vaccon\\
  \affaddr{JSPS--Rikkyo University}\\
  \affaddr{\textsf{vaccon@rikkyo.ac.jp}}
}

@@

\vspace{-1mm}
\ccsdesc[500]{Computing methodologies~Algebraic algorithms}
\printccsdesc

@@

Any computation with $p$-adic fields must work with approximations modulo finite
powers of $p$, and one of the key requirements in designing an algorithm is
an analysis of how the precision of the variables evolve over the computation.
We work with precision models developed by the same authors
\cite[Section~4.2]{caruso-roe-vaccon:14a}, focusing on the lattice and Newton models.
As part of the analysis of the slope factorization algorithm, we describe
how the precision of the quotient and remainder depend on the input polynomials
in Euclidean division.

@@

\bibliographystyle{plain}

% \bib, bibdiv, biblist are defined by the amsrefs package.
\begin{bibdiv}
\begin{biblist}
\tiny

@@

\end{biblist}
\end{bibdiv}

>>>>

\setcopyright{acmlicensed}
\conferenceinfo{ISSAC '16,}{July 19--22, 2016, Waterloo, ON, Canada}
\isbn{978-1-4503-4380-0/16/07}\acmPrice{\$15.00}
\doi{http://dx.doi.org/10.1145/2930889.2930897}

\clubpenalty=10000 
\widowpenalty = 10000

\numberofauthors{3}
\author{
\alignauthor Xavier Caruso\\
  \affaddr{Universit\'e Rennes 1}\\
  \affaddr{xavier.caruso@normalesup.org}
\alignauthor David Roe \\
  \affaddr{University of Pittsburgh}\\
  \affaddr{roed.math@gmail.com}
\alignauthor Tristan Vaccon\\
  \affaddr{JSPS--Rikkyo University}\\
  \affaddr{vaccon@rikkyo.ac.jp}
}

@@

@@

@@

Any $p$-adic computation must work with approximations modulo finite
powers of $p$ and include an analysis of how the precision of the variables evolve over the computation.
We work with precision models developed by the same authors
\cite[Section~4.2]{caruso-roe-vaccon:14a}, focusing on the lattice and Newton models.
As part of the analysis of the slope factorization algorithm, we describe
how the precision of the quotient and remainder depend on the input polynomials
in Euclidean division.

@@

%\bibliographystyle{plain}

\begingroup
\raggedright

% \bib, bibdiv, biblist are defined by the amsrefs package.
\begin{bibdiv}
\begin{biblist}
%\tiny
\vspace*{0.5mm}
\scriptsize

@@

\end{biblist}
\end{bibdiv}
\endgroup
